Fig3

### 2020-04-13 analysis/figure-3.Rmd
candidate hormone degs and corrrs

```{r DEGs}
# summary DEG results from DESeq2
candidateDEGS <- read_csv("../../musicalgenes/data/allDEG.csv") %>%
  select(-X1) %>%
  filter(gene %in% hormonepapergenes)
head(candidateDEGS)

@@

>>>>

```{r fig3, fig.width = 7}
# summary DEG results from DESeq2
candidateDEGS <- read_csv("../../musicalgenes/data/allDEG.csv") %>%
  select(-X1) %>%
  filter(gene %in% hormonepapergenes)
head(candidateDEGS)

@@

# correlations
library(corrr)

plotcorrs <- function(whichtissue){

  x <- candidatevsd %>%
    filter(tissue == whichtissue)  %>%
    pivot_wider(names_from = gene, values_from = counts) %>%
    select(-sex, - tissue, - treatment, -samples) %>%
    correlate()
  print(fashion(x))

  p <- rplot(x, colors = c("#0571b0", "#92c5de", "#f7f7f7","#f7f7f7","#f7f7f7", "#f4a582", "#ca0020")) +
    theme_B3() +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = 1),
          axis.text = element_text(face = "italic")) +
    labs(subtitle = whichtissue)
  return(p)
}

a <- plotcorrs("hypothalamus") 
b <- plotcorrs("pituitary") + theme(axis.text.y = element_blank())
c <- plotcorrs("gonad") + theme(axis.text.y = element_blank())

plot_grid(a,b,c, nrow = 1, rel_widths = c(1.2,1,1))
